### 2019-03-22 README.Rmd

## Bug Fixes in v0.1.3
The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed on the current GitHub master branch:

1. If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values. The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`. Alternatively, you can install the development version of `areal` from GitHub.
2. Some intersections of `sf` geometries will result in geometry collections being created. This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed. The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`. The simplest workaround is to install the development version of `areal` from GitHub.

Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!

>>>>

## Bug Fixes in v0.1.3
The initial CRAN release contains four known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6), [7](https://github.com/slu-openGIS/areal/issues/7), [14](https://github.com/slu-openGIS/areal/issues/14), and [16](https://github.com/slu-openGIS/areal/issues/16)), all of which are fixed on the current GitHub master branch:

1. If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values. The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`. Alternatively, you can install the development version of `areal` from GitHub.
2. Some intersections of `sf` geometries will result in geometry collections being created. This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed. The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`. The simplest workaround is to install the development version of `areal` from GitHub.
3. Interpolation fails if the `sf` geometry column is not named `geometry`. The simplest workaround is to either rename the column to `geometry` before executing `aw_interpolate()`. Alternatively, you can install the development version of `areal` from GitHub.
4. Interpolation with `output = "tibble"` only returns the identification number and the estimated value. If you want other variables from the target data, the simplest workaround is to join the output to the original target data. Alternatively, you can install the development version of `areal` from GitHub.

Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching the first two and [David Blodgett](https://github.com/dblodgett-usgs) for catching the third!

### 2019-03-22 index.Rmd

## Bug Fixes in v0.1.3
The initial CRAN release contains two known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6) and [7](https://github.com/slu-openGIS/areal/issues/7)), both of which are fixed in the current GitHub release:

1. If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values. The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`. Alternatively, you can install the development version of `areal` from GitHub.
2. Some intersections of `sf` geometries will result in geometry collections being created. This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed. The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`. The simplest workaround is to install the development version of `areal` from GitHub.

Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching both of these!

>>>>

## Bug Fixes in v0.1.3
The initial CRAN release contains four known bugs (see Issues [6](https://github.com/slu-openGIS/areal/issues/6), [7](https://github.com/slu-openGIS/areal/issues/7), [14](https://github.com/slu-openGIS/areal/issues/14), and [16](https://github.com/slu-openGIS/areal/issues/16)), all of which are fixed on the current GitHub master branch:

1. If the `tid` and `sid` column names are identical, the interpolated column created by `aw_interpolate()` will consist of all `NA` values. The simplest workaround is to rename either `tid` or `sid` before executing `aw_interpolate()`. Alternatively, you can install the development version of `areal` from GitHub.
2. Some intersections of `sf` geometries will result in geometry collections being created. This appears to be an infrequent issue, but it will result in an error when `aw_interpolate()` is executed. The error will begin with `Warning in st_cast.GEOMETRYCOLLECTION(X[[i]], ...)`. The simplest workaround is to install the development version of `areal` from GitHub.
3. Interpolation fails if the `sf` geometry column is not named `geometry`. The simplest workaround is to either rename the column to `geometry` before executing `aw_interpolate()`. Alternatively, you can install the development version of `areal` from GitHub.
4. Interpolation with `output = "tibble"` only returns the identification number and the estimated value. If you want other variables from the target data, the simplest workaround is to join the output to the original target data. Alternatively, you can install the development version of `areal` from GitHub.

Big thanks to early adopter [Matt Herman](https://github.com/mfherman) for catching the first two and [David Blodgett](https://github.com/dblodgett-usgs) for catching the third!
